\chapter{Conclusion}
\begin{flushleft}
\label{ch:discussion}

\section{Conclusion}
The six months of Internship was a time of experimentation. Internship in an intermediate period of the academic calendar is exceptional from the perspective of our country. From that point of view, this is a matter of glory that during the internship I have passed the best academic period in my life by experiencing real-world technology. It is a matter of grandeur that what I read yesterday at the book is now available to me. Moreover, gathering a vast knowledge about how the real-world works can help me to prepare myself for an upcoming working life for me.
I would like to convey my thanks to the Institute of Information and Communication Technology, Shahjalal University of Science, and Technology for providing me an opportunity to gain an idea of the competitive environment in the professional field. It has certainly lifted my software development skills in terms of design and coding. I now look forward to facing the upcoming challenges of the world.
Orbitax Ltd. is a leading software company in Bangladesh with its innovative and reputed products. So, it was a great opportunity for me to complete my internship period as an effective member of the development of Orbitax. Concerning the assigned project work I had, it was interesting to implement something else that I was taught in my bachelor program. It was interesting to me from different points of view. It was a real pleasure to work in an office with corporate culture. Moreover, working in a team and a friendly official environment made me learn different things. Even though that was something new for me, I was able to change myself with this. Different tools and technologies, experienced human resources, a large range of business domains, innovative products, inspirational and motivating higher authority and friendly environment were the most significant factors to learn professionalism, positive attitude, winning mentality, self- initiative, team strength.

In a word, this internship was a great experience for me. And I hope that this experience will give me inspiration and instruction to build up to me a better future.

\end{flushleft}