\vspace{\fill}
\begin{center}
\begin{large}
\textbf{Acknowledgement}\\
\end{large}
\end{center}
\vspace{20pt}
\begin{flushleft}


An industrial attachment cannot be completed without significant help from others. First we gratefully acknowledge the help and support from our parents, teachers, employers, friends and others, whose support has been invaluable for me. I would like to thank the following people for their contribution in this industrial attachment:\\
\renewcommand{\labelitemi}{$\square$}
 \begin{itemize}
   \item At First, I would like to thank my Institute, Institute of Information Technology,Shahjalal University of Science and Technology for arranging and set the internship program for me. I am also grateful to Orbitax Bangladesh Limited for recruiting me as an intern.
    \item I would like to thank Mohammad Abdullah Al Mumin, Director, Institute of Information and Communication Technology, Shahjalal University of Science and Technology for running the internship program and giving me the opportunity.
    \item I am extremely grateful and remain indebted to CTO of Orbitax Bangladesh Limited Mr. Hasan Shahriar Masud for hiring me as an Intern.
    \item I also thank and gratitude to my Team Leader Mr.Shamim Ahsan Shaon, Senior Software Engineer for his exemplary guidance, monitoring, and constant encouragement throughout this internship. The blessing, help, and guidance given by him from time to time shall carry me a long way in the journey of life on which I am about to embark.
    \item I would like to thank Mr.Plabon Kumar Biswas ,Assoicate Software Engineer for giving me idea, help, support, knowledge in various tasks.
    \item I also Thank Mr. Kousik Deb,Former Associate Software Enginner(Provisional) for helping and co-operatig me during developing time.
    \item I am also thanking honorable teacher to Quazi Istaque Mahmud Rafi and Fazle Mohammed Tausif ,Lecturer, SWE-SUST, for their contribution and hardwork to getting us admit to different companies.
    \item I also like to thank my other seven batch-mate colleagues who are working in Orbitax Bangladesh Limited  for the valuable information provided by them in their respective fields. I am grateful for their cooperation during the period of my internship.
    \item I'm thankful to them who are not mentioned but for their continual constructive criticism and invaluable suggestions and help, which benefited me a lot at my internship.


   
 \end{itemize}
 
  

   


\end{flushleft}
