\vspace{\fill}
\begin{center}
\begin{large}
\textbf{Executive Summary
}\\
\end{large}
\end{center}
\vspace{20pt}
\begin{flushleft}
The internship report highlights the major works carried out by the author in terms of academic and non-academic perspectives. The scope of this document is to identify and describe the analysis carried out, projects completed, experience gained, and focuses on the achievements as an intern.


The author was sent to Orbitax Limited to complete his internship. The author found himself rather lucky by getting the chance to work in such an environment that Orbitax provided and got introduced to some of the new terms, new Technologies, and new Languages. But the most amazing experience was to work in a multicultural work environment.\\\vspace{15pt}

The projects that the author worked in certainly helped him by increasing his practical knowledge depth. The research and development projects were particularly helpful in widening his views regarding different web application development frameworks and mobile application frameworks.\\\vspace{15pt}


Keeping the coding apart, there were also a few more challenges. Some of them were technical and some were non-technical. Coming almost at the end of his internship, the author discovered that some of his communicative and management skills have been improved to a great extent. Besides, there were some vital lessons which will help him in his future jobs.\\\vspace{25pt}


After the internship, the author is more confident, more skilled, and more professional than he was before.

\end{flushleft}